Project Proposal Machine Learning

### 2012-09-17 ProjectProposal/Project.tex
Wording.

\paragraph{Application}
We will obtain our training data from the CoNLL-2003\cite{TjongKimSang:2003:ICS:1119176.1119195} dataset, which contains
data in English and German. Additionally, we may also use the CoNLL-2002 data for Dutch and Spanish.

Named Entity Recognition is a classification problem in which the goal is to correctly predict the named entity types for
the tokens in a text. Table~\ref{table:input} shows the size of the input data and Table~\ref{table:output} shows the types and amount of Named Entity annotations on the input data for German and English.

>>>>

\paragraph{Application}

Named Entity Recognition is a classification problem in which the goal is to correctly predict the named entity types for
the tokens in a text.

We will obtain our training data from the CoNLL-2003\cite{TjongKimSang:2003:ICS:1119176.1119195} dataset, which contains
data in English and German. Additionally, we may also use the CoNLL-2002 data for Dutch and Spanish.  Table~\ref{table:input} shows the size of the input data and Table~\ref{table:output} shows the types and amount of Named Entity annotations on the input data for German and English.
